%Background and Related Work: 20%

\section{Background}
\label{sec:background}

Expand on what the reader needs to know and understand if it necessary to
adequately describe the problem. This may include definitions of terms and
explanations of the present workflow people use to solve the task.

This section should answer the question "What does someone unfamiliar with the
area need to know to understand this project?" Often times this section focuses
on the \textit{domain}. For example, a new visualization for biology data will
explain the type of biology data used, the terminology that will be used to
describe it, the people who use it, and what they hope to learn from it. If
there is no specific domain, the background section may describe general terms
about the data abstraction (e.g. "We define a graph $G = (V, E)$ as..."),
common practices, or other information for visualization researchers who are
not as familiar with this problem in comparison to all the others. 

\subsection{Related Work}
\label{sec:related}

Discuss the work related to your project---include both visualization and
domain-specific references to the problem you're trying to solve. Prominent
related works should be included for this milestone. If you are proposing a
literature review or task taxonomy, this section must include a discussion of
what similar ones exist already and should tie into the motivation. Is the
existing one old enough to be missing many relevant advances?

For example, if my project involves analyzing performance data of distributed
systems, I might want to cite Perfopticon~\cite{Moritz:2015:EuroVis}. If my
project involves designing a new library to support creating new
visualizations, I might want to cite d3js~\cite{d3js}. Note here I am using
keys such as "Moritz:2015:EuroVis" for citations. These refer to the full
definitions in proposal.bib.

ACM Digital Library makes it easy to get bib files for proposal.bib and there
are guides online for citing things like books~\cite{ware:2004:IVP},
theses~\cite{levoy:1989:DSV}, journal articles~\cite{Lorensen:1987:MCA}, and
conference proceedings~\cite{Nielson:1991:TAD}. There's even a format for
miscellaneous references (misc) such as websites and libraries not associated
with a article.

